%-------------------------
% Resume in Latex
% Author : Aras Gungore
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}



%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Shangai Li} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:+8619997955987}{+86 199 9795 5987}
    $|$
    \faAt \hspace{.5pt} \href{mailto:lishangai2003@gmail.com}{lishangai2003@gmail.com}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/lishangai}{GitHub}
    $|$
    \faGlobe \hspace{.5pt} \href{https://lishangai.github.io/}{Portfolio}
    $|$
    \faMapMarker \hspace{.5pt} \href{https://maps.app.goo.gl/hkX3Lx876Cyu9rEx8}{Wuhan, China}
\end{center}



%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart
    
    \resumeEducationHeading
      {Huazhong University of Science and Technology}{Wuhan, China}
      {M.B. Candidate; \textbf{GPA: 86.6/100} (Rank: 7/25)}{Sep 2021 -- Jun 2026}
      {Major in Basic Medicine}{}
    
    \resumeEducationHeading
      {Huazhong University of Science and Technology}{Wuhan, China}
      {B.E. Candidate; \textbf{GPA: 89.6/100}}{Mar 2024 -- Jun 2026}
      {Minor degree in Computer Science and Technology (50 Credits)}{}
      \resumeItemListStart
        \resumeItem{\textbf{Relevant Coursework:} Algorithmic Design \& Analysis (91), Software Engineering (96),  Discrete Mathematics (92), Principles of Databases (92), Computer Networks (95), Principles of Computer Organization (91), Data Structures, Object-Oriented Programming (C++) \textit{etc.}}
      \resumeItemListEnd
      
    \resumeSubheading
      {The University of Texas at Austin}{Austin, TX, USA}
      {Exchange Student; \textbf{GPA: 4/4} (straight A’s)}{Jul 2024 - Aug 2024}
      \resumeItemListStart
        \resumeItem{\textbf{Relevant Coursework:} Python Programming, Data Analytics(R Language)}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%----------- AWARDS & ACHIEVEMENTS -----------

\section{Awards \& Achievements}
 \vspace{2pt}
 \resumeSubHeadingListStart
   \small{\item{
       \textbf{CSC \& Mitacs Undergraduate Research Internship Collaboration Scholarship:}{ Selected as one of $<$200 students nationwide for a fully-funded research internship in Canada (2025)} \\ \vspace{3pt}
       
       \textbf{The 7th Activity and Behavior Computing Challenge, 3rd Place:}{ Secured 3rd Place in an international competition by developing a novel deep learning model for Parkinson's activity recognition. (2025)} \\ \vspace{3pt}
       
       \textbf{Third Prize \& Outstanding Teamwork Award:}{ Awarded for leading a project investigating novel therapeutic responses in pancreatic cancer, presented at the university's flagship medical conference. (Mar 2024)} \\ \vspace{3pt}
       
       \textbf{National High School Physics Competition, Provincial Second Prize:}{ Secured Provincial Second Prize, placing 35th in the theoretical exam portion of the competition. (2020)} \\ \vspace{3pt}
       
       \textbf{Provincial High School Chemistry Competition, First Prize:}{ Achieved First Prize in the provincial-level competition within the Grade 10 cohort. (2019)}
   }}
 \resumeSubHeadingListEnd



%----------- ACADEMIC, RESEARCH & INDUSTRIAL EXPERIENCE -----------

\section{Academic, Research \& Industrial Experience}
 \vspace{3pt}
 \resumeSubHeadingListStart
      \resumeSubheading
      {Long Short-Term Memory Attention for Parkinson’s Activity Recognition}{Wilmington, NC, USA}
      {First Author \& Remote Research Intern}{Jan 2025 -- Mar 2025}
      \resumeItemListStart
        \resumeItem{Conducted this research as part of the selective GEARS (Global Education, Academics, and Research Skills) Program at the University of North Carolina Wilmington.}
        \resumeItem{Engineered a DeepConvLSTM-Attention hybrid model, integrating CNN, LSTM, and attention mechanisms to significantly improve activity recognition accuracy.}
        \resumeItem{Culminated the internship by authoring and submitting a first-author paper to the ABC 2025 international conference, validating the model's superiority over existing methods.}
      \resumeItemListEnd

      \resumeSubheading
      {AI-Driven Computational Study in Cancer Genomics}{St. John's, NL, Canada}
      {Mitacs Globalink Research Intern}{Jun 2025 -- Aug 2025 (Expected)}
      \resumeItemListStart
        \resumeItem{Architected an end-to-end bioinformatics pipeline to resolve a data paradox in cancer genomics, using Kaplan-Meier survival analysis and DESeq2 to statistically define the core problem from TCGA patient data.}
        \resumeItem{Innovatively deployed the GeneFormer foundation model (a Transformer-based model pretrained on 30M+ cells ) for zero-shot \textit{in silico} perturbation, simulating a target gene knockout to generate a novel, testable hypothesis about its transcriptomic impact.}
      \resumeItemListEnd
      
    
      
    \resumeSubheading
      {PBL-Guided Generation of Complete Medical Reasoning Paths}{Wuhan, China}
      {Undergraduate Thesis Researcher}{Jun 2025 -- Oct 2025 (Expected)}
       \resumeItemListStart
       \resumeItem{Designed the `MedPBL-Path' framework to address the limitations of linear reasoning in medical AI, mitigating LLM `hallucination' by anchoring logic in a knowledge graph.}
       \resumeItem{Formalized Problem-Based Learning (PBL) principles into a constrained Breadth-First Search (BFS) algorithm on a knowledge graph, enabling the generation of `differential diagnosis trees' that mimic expert clinical thinking.}
        \resumeItem{Developed a high-quality, `complete' Chain-of- Thought (CoT) dataset designed to fine-tune LLMs for enhanced diagnostic accuracy and clinical decision-support value.}
       \resumeItemListEnd
       
    \resumeSubheading
      {CXCR2-Mediated Response of Pancreatic Cancer Cells to IRE Treatment}{Wuhan, China}
      {Project Leader}{Feb 2023 -- Mar 2024}
      \resumeItemListStart
        \resumeItem{Led a research team to investigate the molecular mechanisms of pancreatic cancer cell response to Irreversible Electroporation (IRE) therapy.}
        \resumeItem{Successfully secured funding and support from the Provincial College Students' Innovation and Entrepreneurship Program.}
        \resumeItem{Authored the project report and presented the findings, winning Third Prize and an Outstanding Teamwork Award at the 2024 Undergraduate Academic Conference.}
      \resumeItemListEnd

 \resumeSubHeadingListEnd
 



%----------- PUBLICATIONS (Final Polished Version) -----------


\section{Publications}
  \vspace{3pt}
  \resumeSubHeadingListStart

    \resumeItem{
      \textbf{Deep Convolutional Long Short-Term Memory Attention for Parkinson's Activity Recognition} \hfill \textit{2025} \\
      \textit{\textbf{Shangai Li}, Demirhan Hilmi\textsuperscript{*}} \\
      \textit{Int. J. Act. Behav. Comput., 2025(2), 1--18}  \href{https://doi.org/10.60401/ijabc.112}{\color{blue}{[DOI]}}
    }
    
    \resumeItem{
      \textbf{Enhancing Healthcare Utilization and Reducing Preventable Hospitalizations: Exploring the Healthcare-Seeking Propensity of Patients with Non-Communicable Diseases in Rural China} \hfill \textit{2025} \\
      \textit{Yanqiu Hou, Wenyu Li, \textbf{Shangai Li}, Linxuan Chen, Jiayu An, Shan Lu\textsuperscript{*}} \\
      \textit{BMC Public Health, 25(1), 323} \href{https://doi.org/10.1186/s12889-025-21542-9}{\color{blue}{[DOI]}}
    }

  \resumeSubHeadingListEnd
%----------- PROJECTS -----------

\section{Projects}
    \vspace{3pt}
    \resumeSubHeadingListStart
      
      \resumeProjectHeading
        {\textbf{MindSpark} $|$ \emph{\href{https://ikjqgcynrhau.sealosbja.site/}{\color{blue}Online Platform}}}{}
          \resumeItemListStart
            \resumeItem{Led the development of an innovative LLM-driven learning platform, taking full ownership from architecture design and full-stack development (Vue 3 + Flask) to the final end-to-end deployment on a Kubernetes-based OS (Sealos). Key contributions include engineering a smart review algorithm, implementing JWT authentication, and integrating the DeepSeek LLM API via sophisticated prompt engineering to generate dynamic knowledge graphs.}
          \resumeItemListEnd
      
    \resumeSubHeadingListEnd
%----------- SKILLS -----------


\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Languages:}{ Python (Proficient), R, C++ (Basic), English (IELTS 6.5)} \\ \vspace{3pt}
        \textbf{Technologies:}{ PyTorch, OpenCV, scikit-learn, Pandas, NumPy, Git, Flask, Kubernetes, Vue, MySQL, } \\ \vspace{3pt}
        \textbf{Methodologies:}{ Deep Learning, Machine Learning, Computer Vision, Medical Image Analysis, Computational Genomics, Medical Reasoning Path Generation, Knowledge Graph Design, Prompt Engineering} \\ \vspace{3pt}
    }}
  \resumeSubHeadingListEnd

%----------- Interdisciplinary Interest -----------
\section{Research Interest}
\resumeSubHeadingListStart
    \resumeItem{Focused on advancing artificial intelligence by developing novel computational methods to solve complex challenges, with a primary focus on driving new discoveries and improving outcomes in healthcare.}
\resumeSubHeadingListEnd


%-------------------------------------------
\end{document}